\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-10-29 analysis/paper/paper.Rmd
paper is knitting now

# Methods {-}
NEON data collection protocols
AOP flights
Plant mapping 
Network of sites and observations (how many? ecoclimatic domains? ecosystem coverage?

@@

Extracted hyperspectral data for all mapped stems at NEON sites
Assumed plant locations don't change over time 
Filtered plants to keep only "live" ones
NEON data products (cite)
Spectrometer orthorectified surface directional reflectance mosaic
Woody plant vegetation structure field based measurements
Mask created for water absorption bands (cite)
Packages neonUtilities, geoNEON, neonhs (cite)

@@

@@

```{r demo-plot, fig.cap="A plot of random numbers"}
plot(rnorm(10))
```

Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

@@

```{r spectra, fig.cap = "", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "spectra_figure_test.png"))
```

@@

```{r excel, fig.cap = "", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
knitr::include_graphics(here::here("analysis", "figures", "honest_work.jpeg"))
```

@@

>>>>

# Methods {-}
NEON data collection protocols
AOP flights
Plant mapping 
Network of sites and observations (how many? ecoclimatic domains? ecosystem coverage?
Figure \@ref(fig:fig-studyArea)

@@

Extracted hyperspectral data for all mapped stems at NEON sites
Figure \@ref(fig:fig-spectraExtracted)
Assumed plant locations don't change over time 
Filtered plants to keep only "live" ones
NEON data products (cite)
Spectrometer orthorectified surface directional reflectance mosaic
Woody plant vegetation structure field based measurements
Mask created for water absorption bands (cite)
Packages neonUtilities, geoNEON, neonhs (cite)

@@

Figure \@ref(fig:fig-honestWork)

@@

@@

```{r fig-studyArea, fig.cap ="Caption", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "study_area.pdf"))
```

@@

```{r fig-honestWork, fig.cap = "Caption", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
knitr::include_graphics(here::here("analysis", "figures", "honest_work.jpeg"))
```

@@

## Figure 3 {-}

```{r fig-spectraExtracted, fig.cap = "Caption", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "spectra_figure_test.png"))
```
